\begin{appendices}
\let\cleardoublepage\clearpage
\chapter{External Materials}
In this project, there were many external materials used for inspiration and development. For this reason, any ROS nodes that are publically available, were not included in this section as the ones used are already mentioned in the report.
\newline\newline
Within the project files:\newline\newline
One of the PhD students within the robotics lab has a github: \url{https://github.com/OMARI1988}. His code provided a lot of the inspiration for mine so parts were taken from his publically hosted projects: \textbf{objectfinder.py} was directly taken from the github, as was some of the setup code for Baxter's movement, adapted from the robotics tabletop/board game code.\newline\newline
Other code used externally tended to be from documentation and tutorials, which are referenced in footnotes throughout the project where necessary.
\chapter{Ethical Issues Addressed}
Whilst in this project, there weren't many ethical issues to address, one has to consider the implications of AI in general with this type of task. In the customer-shopkeeper interaction, Baxter `observes' customers and passers-by throughout the running of the software. In the robotics department, I came across other PhD students having difficulty gaining consent for taking Kinect recordings of skeletons. Whilst Baxter doesn't expressly record them, it could stray into the grey area of whether the person should give their permission to have their images taken/analysed by Baxter in the first place.
\end{appendices}